Quantitative review of the effects of triazole and benzimidazole fungicides on Fusarium head blight and wheat yield in Brazil

### 2017-07-28 article.Rmd
small update in text

It is generally acknowledged that yield responses to a second fungicide spray at post-flowering targeting FHB seem to rarely offset the increased application costs, but the economics are not fully explored (D’Angelo et al. 2014; Mcmullen et al. 1997; Paul et al. 2010). In Brazil, one or two sprays of the triazole and strobilurins mixture (metconazole + pyraclostrobin) and a triazole alone (metconazole) were compared in four trials. Although control efficacy was not improved, yield response was higher with the additional fungicide spray but only when all treatments were combined, including the pre-mix (Spolti et al. 2013). Even though it is not clear whether an additional spray is profitable, two sprays (at flowering and 7-10 days later) are recommended and tested more often than one spray in Brazilian trials. The strategy is likely due to the need of extended protection against foliar diseases provided by pre-mixes of strobilurin and triazole fungicides (Wegulo et al. 2011b).
A narrative review on the use of fungicides in FHB management in Brazil summarized data on mean percent reduction of FHB incidence and index across 19 commercial fungicides applied alone or in combination in eight studies conducted from 1982 to 2009 (Deuner et al. 2011). The overall mean percent control (all fungicides combined) was 50% and 70% for incidence and severity, respectively; however, there was large variation within and among fungicides. Starting in 2011, uniform fungicide trials (UFTs) have been established and conducted yearly by a network of wheat pathologists in the main wheat regions of southern Brazil. The main goal of the cooperative network is to monitor the performance of a common set of fungicides, including current recommendations and new fungicides and using a standard protocol within the season (Santana et al. 2012; 2014; 2016a, b, c).

>>>>

It is usually acknowledged that yield responses to a second fungicide spray at post-flowering targeting FHB seem to rarely offset the increased application costs, but the economics are not fully explored (D’Angelo et al. 2014; Mcmullen et al. 1997; Paul et al. 2010). In Brazil, one or two sprays of the triazole and strobilurins mixture (metconazole + pyraclostrobin) and a triazole alone (metconazole) were compared in four trials. Although control efficacy was not improved, yield response was higher with the additional fungicide spray but only when all treatments were combined, including the pre-mix (Spolti et al. 2013). Even though it is not clear whether an additional spray is profitable, two sprays (at flowering and 7-10 days later) are recommended and tested more often than one spray in Brazilian trials. The strategy is likely due to the need of extended protection against foliar diseases provided by pre-mixes of strobilurin and triazole fungicides (Wegulo et al. 2011b).
A narrative review on the use of fungicides in FHB management in Brazil summarized data on mean percent reduction of FHB incidence and index across 19 commercial fungicides applied alone or in combination in eight studies conducted from 1982 to 2009 (Deuner et al. 2011). The overall mean percent control (all fungicides combined) was 50% and 70% for incidence and severity, respectively; however, there was large variation within and among fungicides. Starting in 2011, uniform fungicide trials (UFTs) have been established and conducted yearly by a network of wheat pathologists in the main wheat regions of southern Brazil. The main goal of the cooperative network is to monitor the performance of a common set of fungicides, including current recommendations and new fungicides and using a standard protocol within the season (Santana et al. 2012; 2014; 2016a, b, c).
